Nanophotonic Computational Design

### 2013-02-18 defense/pres2.tex
Getting there...

\I  Obvious and well-known from a mathematical perspective
    \BI Pre-requisite (200-level) class in optimization curriculum
    \I  Not yet taught (I think) in optics/photonics at Stanford \EI
    \stepwise{\step{
    \BE
    \underbrace{\nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
                -i \omega J }_\text{physics}
    \quad\longrightarrow\quad
    \underbrace{A(z)x = b}_\text{linear algebra}
    \EE
    \begin{align*}
    E &\to x \\
    \epsilon &\to z \\
    \nabla\times\mu_0^{-1}\nabla\times - \omega^2 \epsilon &\to A(z) \\
    -i\omega J &\to b
    \end{align*}
    }
\step{\I  Key: If $A(z)$ is linear in $z$ then $A(z)x=b$ is as well!}
    }

>>>>

\I  Obvious and well-known from a mathematical perspective
    \BI Pre-requisite (200-level) class in optimization curriculum
    \I  Not yet taught (I think) in optics/photonics at Stanford \EI
    \stepwise{\step{
    \BE
    \underbrace{\nabla\times\mu_0^{-1}\nabla\times E - \omega^2 \epsilon E = 
                -i \omega J }_\text{physics}
    \quad\longrightarrow\quad
    \underbrace{A(z)x = b}_\text{linear algebra}
    \EE
    }
    \step{
    \begin{align*}
    E &\to x \\
    \epsilon &\to z \\
    \nabla\times\mu_0^{-1}\nabla\times - \omega^2 \epsilon &\to A(z) \\
    -i\omega J &\to b
    \end{align*}
    }
\step{\I  Key: If $A(z)$ is linear in $z$ then $A(z)x=b$ is as well!}
    }

\oursection{Direct design of structure in 1D}
\I  Chose $x$ (field) and solved for $z$ (structure)
\smallfig{1d_leastsquares}
\pause
\I  Perfect performance but unmanufacturable structure
\nextpage

% \bigfig{1d_regularized}
\smallfig{1d_regularized_1}
\smallfig{1d_regularized_2}
\I  Regularization on $z$ decreases performance 
\nextpage

\I  We know that there exist $x$ which produce well-behaved $z$
\I  However, choosing such $x$ is next to impossible
\I  Therefore, a practical design tool must include $x$-search
\nextpage

\oursection{Iterative design of structure in 1D}
\I  
\I  Insight: Solving for well-behaved $z$ requires fortuitous selection of $x$
\I  Therefore, vary $x$ in order to allow for well-behaved $z$
\smallfig{1d_alternate}
\I  Variation in $x$ allows $z$ to be better behaved
\nextpage

\I  Alternately solve for $x$ and $z$:
    \begin{align*} 
    \minimize_z & \|A(z)x - b\|^2 + \eta_1\|z - z_0\|^2 \\
    \minimize_x & \|A(z)x - b\|^2 + \eta_0\|x - x_0\|^2 
    \end{align*}
\smallfig{1d_alternate}
